modelStudio - perks and features

### 2020-11-22 inst/doc/ms-perks-features.Rmd
version 2.1.0

@@

- `N` is a number of observations used for calculation of
[Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles. 
- `10*N` is a number of observations used for calculation of
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
- `B` is a number of permutation rounds used for calculation of
[Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).

@@

  #:# create modelStudio 
  library(modelStudio)
  library(DALEX)
  model <- glm(survived ~., data = titanic_imputed, family = "binomial")
  explainer <- explain(model,
                       data = titanic_imputed,
                       y = titanic_imputed$survived,
                       label = "Titanic GLM",
                       verbose = FALSE)
  ms <- modelStudio(explainer,
                    widget_id = WIDGET_ID,  #:# use the widget_id 
                    show_info = FALSE)    
  ms$elementId <- NULL                      #:# remove elementId to stop the warning

>>>>

If `new_observation = NULL`, then choose `new_observation_n` observations, evenly spread by the order of `y_hat`. This shall always include the observations, which ids are `which.min(y_hat)` and `which.max(y_hat)`.

```{r eval = FALSE}
modelStudio(explainer, new_observation_n = 5) # default is 3
```

@@

- `N` is a number of observations used for calculation of
[Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles (default is `300`). 
- `N_fi` is a number of observations used for calculation of
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html) (default is `10*N`).
- `B` is a number of permutation rounds used for calculation of
[Shapley Values](https://pbiecek.github.io/ema/shapley.html) (default is `10`).
- `B_fi` is a number of permutation rounds used for calculation of
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html) (default is `B`).

@@

  #:# create modelStudio 
  library(modelStudio)
  library(DALEX)
  model <- glm(survived ~., data = titanic_imputed, family = "binomial")
  explainer <- DALEX::explain(model,
                              data = titanic_imputed,
                              y = titanic_imputed$survived,
                              label = "Titanic GLM",
                              verbose = FALSE)
  ms <- modelStudio(explainer,
                    widget_id = WIDGET_ID,  #:# use the widget_id 
                    show_info = FALSE)    
  ms$elementId <- NULL                      #:# remove elementId to stop the warning
